\documentclass[12pt,a4paper]{report}

\include{settings}

\newcommand{\studyprogramme}{Media Management}
\newcommand{\degreetype}{Bachelor of Arts}
\newcommand{\thesistitle}{
The System and Software Architecture of Applications for the short-term Rental of Electric Scooters
}
\newcommand{\thesissubtitle}{
Analysis of an existing Solution and Evaluation of an exemplarily implemented Back-end Application
}
\newcommand{\thesisauthor}{Jakob Löhnertz}
\newcommand{\thesisdate}{23. Juli 2018}
\newcommand{\thesislocation}{Wiesbaden}
\newcommand{\firstmarker}{Prof.\ Dr.\ Johannes Luderschmidt}
\newcommand{\secondmarker}{Merle Hiort}

\begin{document}

\include{preamble}


\begin{abstract}

The abstract will be added at this place towards the end of the thesis.

\end{abstract}


\tableofcontents



\chapter{Introduction} \label{chap:intro}


\section{Preamble}

The market for electric scooters is on the rise all over the world,
especially in East Asian countries like China. \cn
In Europe though, this market is still very underrepresented in our modern urban lives.\\
While it becomes sort of a commodity in big East Asian cities, in Europe this vehicle
is still more of a status symbol, partially due to its pricing.\cn \\
The definition of the word \emph{scooter} is fairly vague.
Some describe it as a small vehicle with a handlebar and a platform to stand on,
the kind traditionally children were riding.
This paper looks at the \emph{motorcycle-esque type} of a scooter though, and in
particular the electric versions of them.\\
Many pain points of combustion engines vanish with the switch to their electric
counterparts. Certainly, there are also new challenges that arise.
The maintenance of the mechanical system of the whole vehicle becomes easier.
There are less moving parts which makes for less errors.
On the downside, the exchange of the fuel causes the most problems with electric engines.
Of course they utilize batteries instead of fossil fuels as their impetus.
Although the invention of the battery is older than that of the
combustion engine \cn, the technology is still not perfected and sees new
advancements every year. Alas, it also combats many challenges in terms of
safety, cost, capacity, speed of recharging and longevity.\\
All theses challenges are partly to blame for the inferior sales of electric scooters
outside of East Asia. \cn


\section{The market for electric scooters}

Follows...


\section{German electric scooter manufacturer \emph{Kumpan}}

The thesis loosely focuses on the business of German electric scooter manufacturer \emph{Kumpan}.
The company was established in 2009. For their product, they concentrated on three main aspects:
an exterior design ready for the European market, build quality and sufficient cruising radius.
They finished building their first electric scooter in 2010 and are thriving for good products ever since.
The price of their electric scooters is still rather high. Owing to that circumstance,
they came up with smaller, cheaper models as well as a completely different approach.\\
Instead of traditional retail sales they started developing the idea of a
short-term rental service for their scooters. And from many angles it makes sense:
As seen in the last section, the market for the short-term rental of electric scooters
especially in Germany is still minuscule compared to e.g. car or bike sharing.
Meanwhile, the costs for buying an electric scooter are still relatively high.
Lastly, many people will not need such a vehicle for the whole day and would benefit
from more flexibility and parking spots are also a scarcity in our inner cities.
Therefore, \emph{Kumpan} plans to enter the market of short-term electric scooter rentals
in the near future in some form or the other.\\
There are still many aspects to be discussed and determined but one of them
is already set and can be seen as a necessity regardless of the final implementation:
A server back-end application as well as its infrastructure.
\emph{Kumpan} purchased an existing software solution to achieve this.
Beforehand, it was already known though that the software is not feature-complete
for their usage. Thence, it is already planned to augment the software with the missing
features.


\section{Problem and research question}

For the provider, the handling of a short-term rental service
only becomes feasible with the automation of as many processes as possible.
This demands a back-end application ideally paired with a front-end.
Most of the time, ongoing human resource costs make up the biggest percentage
in the expenses of any business.\cn Thus, this demands for less human workforce.
Meanwhile, the upfront expenditures for the software development of
an application are still vast but in the long run, the running expenses are less.
Automation is key in saving costs ultimately. The only cost driver will be maintenance
of the created software.\\
As a consequence, the question should be how to mitigate the maintenance costs
of a software product. The main aspect here is a proper application of software engineering.
Software engineering is defined as: "The application of a systematic, disciplined,
quantifiable approach to the development, operation, and maintenance of software."~\cite{se-ieee}\\
To put this definition into words, software engineering mainly targets
the domains of software architecture, code quality and documentation.
All of these pursue one long-term goal, to achieve a well functioning, maintainable
software product.\\
To conclude, this also leads into the research question of this bachelor thesis:\\
\emph{Which functional modules are necessary for the implementation of an application
for the short-term rental of electric scooters and which considerations need to be made
to integrate additional functionality into an existing legacy software solution for that purpose?}


\section{Motivation}

I am working as a software developer for nearly three years now and programming
is also my biggest hobby. Meanwhile, I noticed that I am about to hit a slight
ceiling with my programming skills. There is still a lot to learn but in my main
languages I became fluent enough to easily implement an idea.
At the same time, I determined that my main weaknesses in developing software are
are not having a thorough knowledge of software architecture and some similar considerations.
Therefore, my main goal in the near future is to gain a lot more knowledge in that field
to overall advance as a software developer.\\
In conclusion, this is also why I chose this topic for my bachelor thesis.
It is currently my personal main field of interest anyways, so it should be
interesting to compose this paper about such a topic.



\chapter{Fundamentals} \label{chap:fundamentals}


\section{Components of a modern software product}

The main aspect of success for such a system is indeed the \emph{magic} behind the scenes
that no customer sees. People just see the electric scooter as the product and
want to be able to ride one on demand by just pushing a button.
The ease of use for the customers and their satisfaction are the main facets
to be considered by the provider of such a service.\\
This, as nearly every modern software product geared towards a general audience,
involves two foundational components – a front-end and a back-end.
On the one hand, the front-end provides the user interface of the product, the façade of the whole.
It is the component the customer interacts with but more importantly it will be
what the users identify the product with.
On the other hand, the back-end is the brain of the software product.
It provides endpoints for the front-end to use and consume. The back-end dictates
what the front-end will do. Meanwhile, it does not determine what it will look like.
If the front-end is unusable the back-end will never be able to fix that as the
front-end becomes the mental representation of the whole product for the customers.
If the back-end behaves sluggish or is prone to errors, the front-end will not be able to save much
by the same token. In the end, both form a synergy with each other.\\
This thesis will shed light on the back-end of such an application.
It will focus on the software architecture of it.
This includes the functionalities that are mandatory and the question on how the product
might come together; from ideas and drafts to written source code.


\section{Necessity of a back-end application}

Follows...


\newpage

% In case the source lists are needed:
%\listoffigures
%\listoftables
%\newpage

% Separate the sources with 'bibtopic'
\bibliographystyle{plain}
\begin{btSect}{offline}
\section*{References}
\btPrintCited
\end{btSect}
\begin{btSect}{online}
\section*{Online Sources}
\btPrintCited
\end{btSect}

\end{document}
